CixPAG

### 2016-10-17 CixPAG/CixPAG-imd.Rmd
Something new

```{r pressure, echo=FALSE}
pt <- retrieve('data/IMD/tp_IMD.1951-2007.nc')
tx <- retrieve('data/IMD/maxT_IMD.1951-2013.nc')
map(pt)
```

>>>>

```{r pressure, echo=FALSE}
pt <- retrieve('data/IMD/tp_IMD.1951-2007.nc')
tx <- retrieve('data/IMD/maxT_IMD.1951-2013.nc')
map(tx)
```

```{r}
Tx.maxjja <- subset(as.4seasons(tx,FUN='max'),it='jja')
eof.tx <- EOF(Tx.maxjja)

Tx.nhd <- annual(tx,FUN='count',threshold=40)
```
